---
title: "Avatar"
author: "Ben Leamon"
date: "15/08/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(tidytext)
library(ggrepel)
```

```{r}
tuesdata <- tidytuesdayR::tt_load('2020-08-11')
```

```{r}
avatar <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-08-11/avatar.csv')
scene_description <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-08-11/scene_description.csv')

```

# Strip out the theme song words.
```{r}
distinct_lines <- avatar%>% distinct(full_text)
theme_song = distinct_lines$full_text[1]

theme_song <- "Water. Earth. Fire. Air. Long ago, the four nations lived together in harmony. Then, everything changed when the Fire Nation attacked. Only the Avatar, master of all four elements, could stop them, but when the world needed him most, he vanished. A hundred years passed, and my brother and I discovered the new Avatar, an airbender named Aang. And although his airbending skills are great, he has a lot to learn before he's ready to save anyone. But I believe Aang can save the world."
first_theme <- "Water. Earth. Fire. Air. My grandmother used to tell me stories about the old days: a time of peace when the Avatar kept balance between the Water Tribes, Earth Kingdom, Fire Nation and Air Nomads. But that all changed when the Fire Nation attacked. Only the Avatar mastered all four elements; only he could stop the ruthless firebenders. But when the world needed him most, he vanished. A hundred years have passed, and the Fire Nation is nearing victory in the war. Two years ago, my father and the men of my tribe journeyed to the Earth Kingdom to help fight against the Fire Nation, leaving me and my brother to look after our tribe. Some people believe that the Avatar was never reborn into the Air Nomads and that the cycle is broken, but I haven't lost hope. I still believe that, somehow, the Avatar will return to save the world."
themes <- c(theme_song, first_theme)

dialogue <- avatar %>%
  filter(!(full_text %in% themes))

```

# Get number of words/sentance
```{r}
a_word <- "([^ ]+)"
no_dots <- " \\.\\.\\."
no_dashes <- " \\-\\-"



dialogue <- dialogue %>%
  mutate(word_number = str_count(character_words, a_word) - str_count(character_words, no_dots) - str_count(character_words, no_dashes))
```

# Add a season-episode id: 
```{r}
dialogue <- dialogue %>%
  unite(season_ep, book_num, chapter_num, sep = ".", remove = FALSE) %>%
  mutate(
    #season_ep = as.double(season_ep)
  )
```

# Possible things to look at: 
## How many times does each character show up?

## What charactars are in what epiodes?
```{r}
characters <- dialogue %>%
  group_by(book, book_num, chapter, season_ep, chapter_num) %>%
  distinct(character)
  
```

```{r}
# Now just to get the number of times a character shows up 
top_characters <- characters %>%
  group_by(character) %>%
  count(character, sort = TRUE)
```


```{r}
characters <- dialogue %>%
  group_by(book, book_num, chapter, season_ep, chapter_num) %>%
  distinct(character) %>%
  inner_join(top_characters, by = "character")
```


```{r}
interested_characters <- characters %>%
  filter(n >1)

ggplot(interested_characters, aes(chapter_num, reorder(character, n))) +
  geom_point()+
  facet_grid(~book_num)
```
I think this would be a nice thing to come back to, maybe make into some sort of poster. It'd be cool to find a way to filter out the generics, and/or make it big enough to print out and display all the information comfortably. Maybe dark blue or parchment background, display the dots in the color of the nation the people are from? Maybe reorder the dots so that people with few appearences early on are higher up, filter the position by number of appearances, then chronologically or something. 

Still, this would be a lot of work, and most of that work would not be actual programming, so I think I'll set that aside for the time being. 


## Episode rankings over time
```{r}
book_names <- as_labeller(c(`1` = "Water", `2` = "Earth",`3` = "Fire"))

dialogue %>%
  distinct(book,book_num, chapter_num, chapter, imdb_rating) %>%
  ggplot(aes(chapter_num, imdb_rating, color = book)) + 
  geom_point()+
  geom_line()+
  facet_wrap(~book_num, labeller = book_names)
  
```

## ep ranking by author
Are there enough writers to make this interesting?
```{r}
dialogue %>%
  count(writer, sort = TRUE)

```
Yes. 
Does the writer have any relationship to IMDB rating
```{r}
dialogue %>%
  ggplot(aes(imdb_rating, writer))+
  geom_boxplot()
```
Hmm...

## Relationship between director and scores? 
How many directors? 
```{r}
dialogue %>%
  distinct(chapter, director) %>%
  count(director, sort = TRUE)
```
Director and IMDB
```{r}
dialogue %>%
  distinct (chapter, director, imdb_rating) %>%
  ggplot(aes(director, imdb_rating))+
  geom_violin()
```
I wonder how much influence the director actually has on quality... 

## does writer or director matter more? 

## Tokenize the words
```{r}
data(stop_words)

tidy_dialogue <- dialogue %>%
  select(character, character_words, season_ep, book, book_num, chapter, chapter_num, imdb_rating) %>%
  mutate(id = row_number())%>%
  unnest_tokens(word, character_words)

tidy_dialogue <- tidy_dialogue %>%
  anti_join(stop_words)

tidy_dialogue
```
## What are the most common words in the series? 
```{r}
tidy_dialogue %>%
  count(word, sort = TRUE)
```
## most common words/ character
```{r}
interested <- c("Aang", "Katara", "Toph", "Sokka", "Zuko", "Iroh")

dialogue_ordered <- tidy_dialogue %>%
  group_by(character) %>%
  #filter(character == "Aang") %>%
  filter(character %in% interested) %>%
  count(word) %>%
  slice_max(order_by = n, n = 10) %>%
  ungroup()%>%
  mutate(character = as.factor(character),
         word = reorder_within(word, n, character))
  
ggplot(dialogue_ordered, aes(n, word))+
    geom_col()+
    facet_wrap(~character, scales = "free")+
    scale_y_reordered()
```


##most common words/character (non-main charctar)

##charactar words/episode

## words/episode
```{r}
tidy_dialogue %>%
  count(chapter, sort = TRUE)
```


```{r}
ep_words <- tidy_dialogue %>%
  add_count(chapter)%>%
  distinct(chapter, .keep_all = TRUE) 
  

ggplot(ep_words, aes(chapter_num, n))+
  geom_point() +
  geom_line()+
  facet_wrap(~book_num)+
  labs(
    title = "Words per episode"
  )
```

```{r}
ggplot(ep_words, aes(n, imdb_rating))+
  geom_point()+
  geom_smooth()
```

# Moving to the final charts: 
```{r}
nations_palette <- c("#3a7714","#a20100","#004f97","#fa5e00")
```
## Episode rankings over time: 
```{r}
width <- 9

ranking_dialogue <- dialogue%>%
  distinct(book,book_num, chapter_num, chapter, imdb_rating)

highest_eps <- ranking_dialogue %>%
  group_by(book) %>%
  slice_max( order_by = imdb_rating, n = 2)

lowest_eps <- ranking_dialogue %>%
  group_by(book) %>%
  slice_min(order_by = imdb_rating, n = 2)

theme_set(theme_minimal())
theme <- theme_update(
  text = element_text(family = "Fira Mono"),
  plot.title = element_text(family = "Fira Sans Medium"),
  plot.title.position = "plot",
  legend.position = "none",
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  plot.caption = element_text(family = "Fira Mono"),
  plot.margin = margin(20,20,20,20)
  #plot.background = element_rect(fill = "#eceff4")
)

book_names <- as_labeller(c(`1` = "Water", `2` = "Earth",`3` = "Fire"))
  
ggplot(ranking_dialogue, aes(chapter_num, imdb_rating, color = book)) + 
  geom_point()+
  #geom_line()+
  scale_color_manual(values = nations_palette)+
  expand_limits(y=10)+
  facet_wrap(~book_num, labeller = book_names)+
  geom_text_repel(data = subset(ranking_dialogue, chapter %in% highest_eps$chapter | chapter %in% lowest_eps$chapter), 
                  mapping = aes(label = chapter),
                  box.padding = 1,
                  size = 3,
                  color = "black",
                  direction = "y") +
  labs(title = "Which episodes have the highest ratings?",
       subtitle = "Top-rated episodes in each season",
       caption = "Data: appa | Plot: Ben Leamon | Ratings from IMDB") #+ 
  ggsave(here::here("2020-08-11-avatar/figs/rankings.png"),device = "png", type = "cairo", width = width, height = width*0.618, dpi = 300)
  
```

## Words per episode
```{r}


ep_words <- tidy_dialogue %>%
  add_count(chapter)%>%
  distinct(chapter, .keep_all = TRUE) 
  
chatty <- ep_words %>% 
  group_by(book) %>% 
  slice_max(order_by = n, n = 2)

quiet <- ep_words %>% 
  group_by(book) %>% 
  slice_min(order_by = n, n = 2)

ggplot(ep_words, aes(chapter_num, n, color = book))+
  geom_point() +
  #geom_line()+
  geom_text_repel(data = subset(ep_words, chapter %in% chatty$chapter | 
                                  chapter %in% quiet$chapter), 
                  aes(label = chapter),
                  box.padding = 1,
                  size = 3,
                  color = "black") +
  scale_color_manual(values = nations_palette)+
  expand_limits(y = 1000)+
  facet_wrap(~book_num, labeller = book_names)+
  labs(title = "Which episodes have the most and least dialogue?",
       subtitle = "Total words per episode",
       caption = "Data: appa | Plot: Ben Leamon"
  )+
  ggsave(here::here("2020-08-11-avatar/figs/words.png"),device = "png", type = "cairo", width = width, height = width*0.618, dpi = 300)
```

## Most common words by character: 
```{r}
interested <- c("Aang", "Katara", "Toph", "Sokka", "Zuko", "Iroh")

dialogue_ordered <- tidy_dialogue %>%
  group_by(character) %>%
  #filter(character == "Aang") %>%
  filter(character %in% interested) %>%
  count(word) %>%
  slice_max(order_by = n, n = 10) %>%
  ungroup()%>%
  mutate(character = as.factor(character),
         word = reorder_within(word, n, character))
  
ggplot(dialogue_ordered, aes(n, word))+
    geom_col(fill = "#4D8FAC")+
    #scale_fill_manual(values = nations_palette)+
    facet_wrap(~character, scales = "free")+
    scale_y_reordered()+
    labs(title = "Most common words spoken by each character",
       caption = "Data: appa | Plot: Ben Leamon")+
    ggsave(here::here("2020-08-11-avatar/figs/common_words.png"),device = "png", type = "cairo", width = width, height = width*0.618, dpi = 300)
```

