---
title: "2020-09-29-beyonce-lyrics-analysis"
author: "Ben Leamon"
date: "2020-10-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 2020-09-29 Tidy Tuesday: Beyonce Lyrics
I've been learning about text analysis using Tidy Text Mining with R (https://www.tidytextmining.com/), and thought I'd apply what I've learned so far to Beyoncé's song lyrics. If you'd like to check out the code for this project, you can find it all on my github(https://github.com/benleamon/tidy-tuesday/tree/master/2020-09-29-beyonce-lyrics).
```{r}
tuesdata <- tidytuesdayR::tt_load("2020-09-29")
bey_lyrics <- tuesdata$beyonce_lyrics
```

```{r}
library(tidyverse)
library(tidytext)
library(beyonce)
```

```{r}
data(stop_words)

tidy_lyrics <- bey_lyrics %>%
  unnest_tokens(word, line) %>%
  anti_join(stop_words)

tidy_lyrics
```
The first step was creating a list of stop-words- words that I don't want to use in my analysis. Since I'm looking at song lyrics, there are a lot of non-standard or otherwise meaningless words that I want to remove. I may have missed some, but in the end I purged: "ooh", "oooh", "wwith", "til", "i've", "i'm", "ahh", "wooooooo", "wooooo", "woooooo", "ooooohh", "aww", "uh", "ooh", "da", "woo", "halo", "woah", "whoa", "ohh", and the exceedingly long , "ohhhoooooooooooooooooooooowww".

```{r}
dist_words <- distinct(tidy_lyrics, word)

custom_stop_words <- bind_rows(tibble(word = c("ooh", "oooh", "wwith", "til", "i've", "i'm", "ahh", "wooooooo", "wooooo", "woooooo", "ooooohh", "ohhhoooooooooooooooooooooowww", "aww", "uh", "ooh", "da", "woo", "halo", "woah", "whoa", "ohh"), lexicon = c("custom")), stop_words)

tidy_lyrics <- tidy_lyrics %>%
  anti_join(custom_stop_words)

```
Next I wanted to look at what words were used most frequently in Beyoncé's songs. 
```{r}
width <- 10
title_font <- "Fira Sans Medium"
main_font <- "Fira Mono"

theme_set(theme_minimal())
theme <- theme_update(
  text = element_text(family = main_font),
  plot.title = element_text(family = title_font, size = 14),
  plot.title.position = "plot",
  legend.position = "none",
  axis.title = element_text(size = 10),
  axis.text = element_text(size = 10),
  #axis.title.x = element_blank(),
  #axis.title.y = element_blank(),
  plot.caption = element_text(family = main_font, size = 8),
  plot.margin = margin(20,20,20,20)
  #plot.background = element_rect(fill = "#eceff4")
)

p <- tidy_lyrics %>%
  count(word, sort = TRUE) %>%
  slice_max(order_by = n, n = 30) %>%
  mutate(word = fct_reorder(word, n))%>%
  ggplot(aes(n , word))+
  geom_col(fill = beyonce_palette(129)[2])+
  labs(
    title = "What words are most common in Beyoncé songs?",
    caption = "Data: Tidy Tuesday | Plot: Ben Leamon", 
    x = "n",
    y = "Word"
  ) 

ggsave(filename = here::here("2020-09-29-beyonce-lyrics/figs/fig-1_common_words.png"), plot = p, device = "png", type = "cairo", width = 6, height = 6,units = "in", dpi = 300)

p
```
I don't listen Beyoncé too frequently, but none of this seems that surprising. Next I wanted to see what were the most frequent postive and negative words in her songs. 

```{r}
tidy_lyrics %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  group_by(sentiment) %>%
  slice_max(order_by = n, n = 20) %>%
  ungroup() %>%
  mutate(word = reorder_within(word, n, sentiment)) %>%
  ggplot(aes(word, n, fill = sentiment)) + 
  geom_col() + 
  facet_wrap(~sentiment, ncol = 2, scales = "free") + 
  coord_flip()+ 
  scale_x_reordered()+
  scale_fill_manual(values = c(beyonce_palette(129)[6],beyonce_palette(129)[4]))+
  labs(
    title = "Most common positive and negative words in Beyoncé lyrics",
    caption = "Data: Tidy Tuesday | Plot: Ben Leamon", 
    x = "n",
    y = "Word"
  ) +
  ggsave(filename = here::here("2020-09-29-beyonce-lyrics/figs/fig-2_postive_v_negative.png"), device = "png", type = "cairo", width = 6, height = 6,units = "in", dpi = 300)

```
She uses love *a lot*; it's by far the most common positive word in her songs. Some of the negative words seem a bit suspect however. Lots of them seem negative on their own, but can take on different meanings when used in conjunction with other words. If crazy was used, for example, in the context of "crazy in love", there's nothing negative about it. "Bad" and "damn" have similarly ambiguous uses. We'll come back to this momentarily. First, let's do a little more analysis based on single words. 

What emotions are most common in Beyonce songs? 
```{r}
lyrics_nrc <- tidy_lyrics %>% 
  inner_join(get_sentiments("nrc"))

lyrics_nrc %>%
  count(sentiment, sort = TRUE) %>%
  ggplot(aes(sentiment, n, fill = sentiment)) + 
  geom_col()+
  labs(
    title = "What sentiments are most common in Beyoncé lyrics?",
    caption = "Data: Tidy Tuesday | Plot: Ben Leamon", 
    x = NULL,
    y = "n"
  )+
  scale_fill_manual(values = beyonce_palette(82))+
  ggsave(filename = here::here("2020-09-29-beyonce-lyrics/figs/fig-3_common_sentiments.png"), device = "png", type = "cairo", width = width, height = width*0.618,units = "in", dpi = 300)
  
```
We can see that there's lots of positivity, negativity, and joy in a lot of Beyoncé's songs, which to a novice like me isn't that surprising. Some of the bases for these sentiments seems more solid than others however. 
What words are contributing to each sentiment? 
```{r}
lyrics_nrc %>%
  group_by(sentiment) %>%
  count(word) %>%
  slice_max(order_by = n, n = 5) %>%
  ungroup()%>%
  mutate(word = reorder_within(word,n,sentiment))%>%
  ggplot(aes(word, n, fill = sentiment))+
  geom_col(fill = beyonce_palette(129)[4])+
  facet_wrap(~sentiment, ncol = 4, scales = "free")+
  scale_x_reordered()+
  #scale_fill_manual(values = beyonce_palette(89))+
  labs(
    title = "Most common words for each sentiment:",
    caption = "Data: Tidy Tuesday | Plot: Ben Leamon", 
    x = "n",
    y = "Word"
  )+
  ggsave(filename = here::here("2020-09-29-beyonce-lyrics/figs/fig-4_words_by_sentiment.png"), device = "png", type = "cairo", width = width, height = width*0.618,units = "in", dpi = 300)
```
While some of the words contributing to each sentiment make sense, positive, joy, and trust for example, especially in the context of song lyrics some seem more shaky. Alternate meanings for "slay" come to mind. Is she talking about murdering people, or using it to connote excellence? 

Now let's look at which songs are most closely associated with which sentiments. 
```{r}
lyrics_nrc %>%
  group_by(sentiment) %>%
  count(song_name) %>%
  slice_max(order_by = n, n=5) %>%
  ungroup() %>%
  mutate(song_name = reorder_within(song_name, n, sentiment)) %>%
  ggplot(aes(song_name, n)) +
  geom_col(fill = beyonce_palette(129)[5])+
  facet_wrap(~sentiment, ncol =1, scales = "free")+
  coord_flip()+
  scale_x_reordered()+
  labs(
    title = "What songs are associated with each sentiment?"
  )
  ggsave(filename = here::here("2020-09-29-beyonce-lyrics/figs/fig-5_sentiment_by_song.png"), device = "png", type = "cairo", width = width, height = (width*0.618)*2,units = "in", dpi = 300)
```


Finally, I wanted to look at bigrams, or pairs of words. Specifically, I was inerested in bigrams where the first word in the pair negates the second. 
```{r}
bey_bigrams <- bey_lyrics %>%
  unnest_tokens(bigram, line, token = "ngrams", n = 2) %>%
  separate (bigram, c("word1", "word2"), sep = " ", remove = FALSE)

filtered_bigrams <- bey_bigrams %>%
  filter(!word1 %in% custom_stop_words$word) %>%
  filter(!word2 %in% custom_stop_words$word)

filtered_bigrams %>%
  count(word1, word2, sort = TRUE)


```

```{r}
bey_lyrics %>%
  unnest_tokens(word, line)%>%
  filter(word == "not")
```

```{r}
bing <- get_sentiments("bing")
afinn <- get_sentiments("afinn")

negation_words <- c("without", "not","no", "don't", "never", "can't", "won't")

negated_bigrams <- bey_bigrams %>%
  filter(word1 %in% negation_words) %>%
  inner_join(afinn, by = c(word2 = "word")) %>%
  count(word1, word2, value, sort = TRUE)

negated_bigrams

# negated_bigrams %>%
#   arrange(desc(abs(effect))) %>%
#   head(20) %>%
#   mutate(word2 = reorder(word2, effect)) %>%
#   ggplot(aes(word2, effect, fill = effect > 0)) + 
#   geom_col(show.legend = FALSE)+
#   coord_flip()

negated_bigrams %>%
  mutate(effect = value * n) %>%
  group_by(word1) %>%
  slice_max(order_by = effect, n = 10) %>%
  ungroup() %>%
  mutate(word2 = reorder_within(word2, effect, word1)) %>%
  ggplot(aes(word2, effect, fill = effect > 0))+
  geom_col(show.legend = FALSE)+
  coord_flip()+
  facet_wrap(~word1, scales = "free")+
  scale_x_reordered()+
  scale_fill_manual(values = c(beyonce_palette(129)[6],beyonce_palette(129)[4]))+
  labs(
    title = "How are negated words influencing sentiment scores?",
    subtitle = "Negated bigrams can make lyrics seem more positive or more negative than they are.",
    caption = "Data: Tidy Tuesday | Plot: Ben Leamon", 
    x = "Effect",
    y = "Negated word"
  )+
  ggsave(filename = here::here("2020-09-29-beyonce-lyrics/figs/fig-6_negated_bigrams.png"), device = "png", type = "cairo", width = width, height = width*0.618,units = "in", dpi = 300)
```
Positive (blue) values represent combinations that make the songs seem falsely positive, and negative (red) values make the songs seem falsely negative, when analyzing individual words alone. In short, her songs are a lot less positive than they seemed at first glance!

I also wanted to have a look at some of the top bigrams, and the relationships between them. 


[TO DO] Look at some of the suspect words from the sentiments above. For example crazy in the negative ones. If it's in the context of crazy about you, for example, that could be skewing our analysis. 
Look at: 
- crazy, bad, fall, slow, blow (from overall negative words/ Bing)
- Slay, bout (anger), black (sadness), love(lots of positives) (NRC)

OK let's look at the network of all the bigrams. 
```{r}
library(igraph)
library(ggraph)

bigram_totals <- filtered_bigrams %>%
  filter(!is.na(word1)) %>%
  count(word1, word2, bigram,sort = TRUE)

bigram_graph <- bigram_totals %>%
  filter(n > 20) %>%
  graph_from_data_frame()

a <- grid::arrow(type = "closed", length = unit(.1, "inches"))

ggraph(bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), arrow = a, show.legend = FALSE)+
  geom_node_point(color = beyonce_palette(129)[4])+
  geom_node_text(aes(label = name), vjust = 1, hjust = 1)+
  theme_void()+
  theme(plot.margin = margin(20,20,20,20),
        text = element_text(family = main_font),
        plot.title = element_text(family = title_font, size = 14),
        plot.title.position = "plot")+
  labs(
    title = "What words are often connected?",
    subtitle = "Connections between the top twenty bigrams",
    caption = "Arrow darkness corresponds to strength of association | Data: Tidy Tuesday | Plot: Ben Leamon", 
    x = NULL,
    y = NULL
  )
  ggsave(filename = here::here("2020-09-29-beyonce-lyrics/figs/fig-7_bigram_connections.png"), device = "png", type = "cairo", width = width, height = width*0.618,units = "in", dpi = 300)
```
Lots of words are bigrams with themselves, for example "run", "whoa", "ma", "waiting", and "wow". This was not the case when I learned how to make this kind of graph with text from eighteenth century novel. In the context of song lyrics, however this makes sense. Lyrics have lots of repeated words. It's also interesting that the bigrams aren't more connected. Again, I suppose this makes sense. Songs will have lots of often-repeated identical combinations of words, especially in the chorus. This is just speculation on my part however, it would be interesting to compare this to other artists. 

There are also some bigrams that show a relationship in both directions. I suspect that these are phases from the chorus that are repeated back to back. For example, the bigram "gettin" "bodied". In the song "Get Me Bodied", "Gettin' bodied" is repeated multiple times. Because line breaks aren't taken into account when creating the bigrams,  both "gettin bodied" and "bodied gettin" appear. This is a weakness in the analysis, since combinations of words that often appear at the end and beginning of lines would be considered bigrams, despite a listener not necessarily considering them connected. 

