---
title: "2020-09-29-beyonce-lyrics-analysis"
author: "Ben Leamon"
date: "2020-10-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 2020-09-29 Tidy Tuesday: Beyonce Lyrics
```{r}
tuesdata <- tidytuesdayR::tt_load("2020-09-29")
bey_lyrics <- tuesdata$beyonce_lyrics
```

```{r}
library(tidyverse)
library(tidytext)
```

```{r}
data(stop_words)

tidy_lyrics <- bey_lyrics %>%
  unnest_tokens(word, line) %>%
  anti_join(stop_words)

tidy_lyrics
```
```{r}
dist_words <- distinct(tidy_lyrics, word)

custom_stop_words <- bind_rows(tibble(word = c("ooh", "oooh", "wwith", "til", "i've", "i'm", "ahh", "wooooooo", "wooooo", "woooooo", "ooooohh", "ohhhoooooooooooooooooooooowww", "aww", "uh", "ooh", "da", "woo", "halo", "woah", "whoa", "ohh"), lexicon = c("custom")), stop_words)

tidy_lyrics <- tidy_lyrics %>%
  anti_join(custom_stop_words)

```
Popular words
```{r}
width <- 9

theme_set(theme_minimal())
theme <- theme_update(
  text = element_text(family = "Fira Mono"),
  plot.title = element_text(family = "Fira Sans Medium"),
  plot.title.position = "plot",
  legend.position = "none",
  #axis.title.x = element_blank(),
  #axis.title.y = element_blank(),
  plot.caption = element_text(family = "Fira Mono"),
  plot.margin = margin(20,20,20,20)
  #plot.background = element_rect(fill = "#eceff4")
)

tidy_lyrics %>%
  count(word, sort = TRUE) %>%
  slice_max(order_by = n, n = 30) %>%
  mutate(word = fct_reorder(word, n))%>%
  ggplot(aes(n , word))+
  geom_col()+
  labs(
    title = "What words are most common in Beyoncé songs?",
    caption = "Data: Tidy Tuesday | Plot: Ben Leamon", 
    x = "n",
    y = "Word"
  )
```

Positive and negative words
```{r}
tidy_lyrics %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  group_by(sentiment) %>%
  slice_max(order_by = n, n = 20) %>%
  ungroup() %>%
  mutate(word = reorder_within(word, n, sentiment)) %>%
  ggplot(aes(word, n)) + 
  geom_col() + 
  facet_wrap(~sentiment, ncol = 2, scales = "free") + 
  coord_flip()+ 
  scale_x_reordered()+
  labs(
    title = "Most common positive and negative words in Beyoncé lyrics",
    caption = "Data: Tidy Tuesday | Plot: Ben Leamon", 
    x = "n",
    y = "Word"
  )

```

What emotions are most common in Beyonce songs? 
```{r}
lyrics_nrc <- tidy_lyrics %>% 
  inner_join(get_sentiments("nrc"))

lyrics_nrc %>%
  count(sentiment, sort = TRUE) %>%
  ggplot(aes(sentiment, n)) + 
  geom_col()+
  labs(
    title = "What sentiments are most common in Beyoncé lyrics?",
    caption = "Data: Tidy Tuesday | Plot: Ben Leamon", 
    x = NULL,
    y = "n"
  )
  
```

What words are contributing to each sentiment? 
```{r}
lyrics_nrc %>%
  group_by(sentiment) %>%
  count(word) %>%
  slice_max(order_by = n, n = 5) %>%
  ungroup()%>%
  mutate(word = reorder_within(word,n,sentiment))%>%
  ggplot(aes(word, n))+
  geom_col()+
  facet_wrap(~sentiment, ncol = 4, scales = "free")+
  coord_flip()+
  scale_x_reordered()+
  labs(
    title = "Most common words for each sentiment:",
    caption = "Data: Tidy Tuesday | Plot: Ben Leamon", 
    x = "n",
    y = "Word"
  )
```

Now let's look at which songs are most closely associated with which sentiments. 
```{r}
lyrics_nrc %>%
  group_by(sentiment) %>%
  count(song_name) %>%
  slice_max(order_by = n, n=5) %>%
  ungroup() %>%
  mutate(song_name = reorder_within(song_name, n, sentiment)) %>%
  ggplot(aes(song_name, n)) +
  geom_col()+
  facet_wrap(~sentiment, ncol =2, scales = "free")+
  coord_flip()+
  scale_x_reordered()
```
Lemonade Film (Script) seems to be coming in at the top of many of the negative emotions. 

Let's do a little n-gram analysis. 

```{r}
bey_bigrams <- bey_lyrics %>%
  unnest_tokens(bigram, line, token = "ngrams", n = 2) %>%
  separate (bigram, c("word1", "word2"), sep = " ", remove = FALSE)

filtered_bigrams <- bey_bigrams %>%
  filter(!word1 %in% custom_stop_words$word) %>%
  filter(!word2 %in% custom_stop_words$word)

filtered_bigrams %>%
  count(word1, word2, sort = TRUE)


```

Examine bigrams where one word is preceded by something like "not" or another negation.
Look at: 
- not
- don't
```{r}
bey_lyrics %>%
  unnest_tokens(word, line)%>%
  filter(word == "not")
```
OK let's have a look: 

```{r}
bing <- get_sentiments("bing")
afinn <- get_sentiments("afinn")

negation_words <- c("without", "not","no", "don't", "never", "can't", "won't")

negated_bigrams <- bey_bigrams %>%
  filter(word1 %in% negation_words) %>%
  inner_join(afinn, by = c(word2 = "word")) %>%
  count(word1, word2, value, sort = TRUE)

negated_bigrams

# negated_bigrams %>%
#   arrange(desc(abs(effect))) %>%
#   head(20) %>%
#   mutate(word2 = reorder(word2, effect)) %>%
#   ggplot(aes(word2, effect, fill = effect > 0)) + 
#   geom_col(show.legend = FALSE)+
#   coord_flip()

negated_bigrams %>%
  mutate(effect = value * n) %>%
  group_by(word1) %>%
  slice_max(order_by = effect, n = 10) %>%
  ungroup() %>%
  mutate(word2 = reorder_within(word2, effect, word1)) %>%
  ggplot(aes(word2, effect, fill = effect > 0))+
  geom_col(show.legend = FALSE)+
  coord_flip()+
  facet_wrap(~word1, scales = "free")+
  scale_x_reordered()
```
Note: the blue words make the songs seem eroniously positive, and the red words make it seem eroniously negative. In short, her songs are a lot less positive than they seem at first glance!




[TO DO] Look at some of the suspect words from the sentiments above. For example crazy in the negative ones. If it's in the context of crazy about you, for example, that could be skewing our analysis. 
Look at: 
- crazy, bad, fall, slow, blow (from overall negative words/ Bing)
- Slay, bout (anger), black (sadness), love(lots of positives) (NRC)

OK let's look at the network of all the bigrams. 
```{r}
library(igraph)
library(ggraph)

bigram_totals <- filtered_bigrams %>%
  filter(!is.na(word1)) %>%
  count(word1, word2, bigram,sort = TRUE)

bigram_graph <- bigram_totals %>%
  filter(n > 20) %>%
  graph_from_data_frame()

a <- grid::arrow(type = "closed", length = unit(.1, "inches"))

ggraph(bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), arrow = a, show.legend = FALSE)+
  geom_node_point(color = "cornflowerblue")+
  geom_node_text(aes(label = name), vjust = 1.5, hjust = 1.5)+
  theme_void()
```
Interesting. Lots of words are bigrams with themselves, for example "run", "whoa", "ma", "waiting", and "wow". This makes sense, song lyrics have ltos of repeated words. The other thing that's interesting is that the bigrams aren't more connected. Again, I suppose this makes sense. Songs will have lots of often-repeated combinations of words, especially in the chourus.
There are also some bigrams that show a relationship in both directions. I suspect that these are phases from the chorus that are repeated back to back. For example, the bigram "gettin" "bodied". In the song "Get Me Bodied", "Gettin' bodied" is repeated over and over. Because line breaks aren't taken into account when creating the bigrams, the both "gettin bodied" and "bodied gettin" appear. This is a weakness in the analysis, since combinations of words that often appear at the end and beginning of lines would be considered bigrams, despite a listener not necessarily considering them connected. 

