---
title: "food-consumption-working"
author: "Ben Leamon"
date: "26/02/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Import data from GitHub: 
```{r}
tuesdata <- tidytuesdayR::tt_load('2020-02-18')
```
Now I think we need to clean this up and make a proper dataframe. 
```{r}
library(tidyverse)
library(janitor)
library(rvest)

# Credit to Kasia and minorly edited to create output file and test plot
# Blog post at https://r-tastic.co.uk/post/from-messy-to-tidy/

url <- "https://www.nu3.de/blogs/nutrition/food-carbon-footprint-index-2018"

# scrape the website
url_html <- read_html(url)

# extract the HTML table
whole_table <- url_html %>% 
  html_nodes('table') %>%
  html_table(fill = TRUE) %>%
  .[[1]]

table_content <- whole_table %>%
  select(-X1) %>% # remove redundant column
  filter(!dplyr::row_number() %in% 1:3) # remove redundant rows

raw_headers <- url_html %>%
  html_nodes(".thead-icon") %>%
  html_attr('title')

tidy_bottom_header <- raw_headers[28:length(raw_headers)]
tidy_bottom_header[1:10]

raw_middle_header <- raw_headers[17:27]
raw_middle_header

tidy_headers <- c(
  rep(raw_middle_header[1:7], each = 2),
  "animal_total",
  rep(raw_middle_header[8:length(raw_middle_header)], each = 2),
  "non_animal_total",
  "country_total")

tidy_headers

combined_colnames <- paste(tidy_headers, tidy_bottom_header, sep = ';')
colnames(table_content) <- c("Country", combined_colnames)
glimpse(table_content[, 1:10])

long_table <- table_content %>%
  # make column names observations of Category variable
  tidyr::pivot_longer(cols = -Country, names_to = "Category", values_to = "Values") %>%
  # separate food-related information from the metric
  tidyr::separate(col = Category, into = c("Food Category", "Metric"), sep = ';')

glimpse(long_table)

tidy_table <- long_table %>%
  tidyr::pivot_wider(names_from = Metric, values_from = Values) %>%
  janitor::clean_names('snake')

glimpse(tidy_table)

final_table <- tidy_table %>%
  rename(consumption = 3,
         co2_emmission = 4) %>%
  filter(!stringr::str_detect(food_category, "total"))

clean_table <- final_table %>% 
  mutate_at(vars(consumption, co2_emmission), parse_number)

clean_table %>% 
  write_csv("/Users/benleamon/Documents/Infographics/projects/tidy-tuesday/2020-02-18-food-consumption/data/food-consumption-data.csv")

clean_table %>% 
  ggplot(aes(x = fct_reorder(food_category, consumption), y = consumption, color = country)) +
  geom_jitter() +
  theme(legend.position = "none") +
  coord_flip()

```
Import that dataframe: 
```{r}
library(here)
food_data <- read_csv(here("2020-02-18-food-consumption/data/food-consumption-data.csv"))
```

##Scaffodling for the project: 
- Everything we eat emits c02 and contributes to climate change.
- The amount of c02 every country's food supply generates is different. (Countries give off different amounts of Co2.)
- Graph of countries x total c02/person from food supply 
- 

## Generate some Graphs, see what they look like.
```{r}
data_subset <- subset(food_data, country %in% c("Japan"))
p <- ggplot(data = data_subset, aes(x = fct_reorder(food_category,-co2_emmission),
                                  y = co2_emmission))
p + geom_point() + 
  theme_minimal()
```

Graph of all countries' emissions 
```{r fig.width=8, fig.height=12}
emmissions_by_country <- food_data %>%
  group_by(country) %>%
  summarise(total = sum(co2_emmission))
  #Change "united kingdom" in emmissions_by_country to "UK", as it appears in world.
emmissions_by_country$country <- as.character(emmissions_by_country$country)
emmissions_by_country$country[emmissions_by_country$country == "United Kingdom"] <- "UK"
emmissions_by_country$country <- as.factor(emmissions_by_country$country)

p <- ggplot(data = emmissions_by_country, aes(fct_reorder(country,total),total))
p1 <- p + geom_point()+
  coord_flip() + 
  theme_minimal()
p1
```


Save the graphic
```{r}
library(here)
ggsave(here("2020-02-18-food-consumption/figures", "co2_diet.pdf"), plot = p1, height = 15, width = 8)

```


Setting up our data for the map: 
```{r}
library(maps)
world <- map_data("world")

world_emmissions <- left_join(world, emmissions_by_country, by = c("region" = "country"))
```

```{r}
theme_map <- function(base_size = 9, base_family = ""){
  require(grid)
  theme_bw(base_size = base_size, base_family = base_family) %+replace%
    theme(axis.line = element_blank(),
          axis.text = element_blank(),
          axis.ticks = element_blank(),
          axis.title = element_blank(),
          panel.background = element_blank(),
          panel.border = element_blank(),
          panel.grid = element_blank(),
          panel.spacing = unit(0, "lines"),
          plot.background = element_blank(),
          legend.justification = c(0,0),
          legend.position = c(0,0)
          )
}
```


```{r}
p <- ggplot(data = world_emmissions, 
            aes(x = long, y = lat, group = group, fill = total))
p + geom_polygon( color = "gray90", size = 0.1)+ 
  coord_map(projection = "mollweide",xlim=c(-180,180)) +
  scale_fill_continuous(na.value = "gray") + 
  labs(title = "Co2 Emmissions from Diet")+
  theme_map()+
  labs(fill = "Kg Co2/person/year")
```

