---
title: "2021-04-20-netflix-analysis"
author: "Ben Leamon"
date: "2021-04-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 2021-04-20 Tidy Tuesday: Netflix
```{r}
tuesdata <- tidytuesdayR::tt_load("2021-04-20")
netflix <- tuesdata$netflix_titles
```
```{r}
proj_path <- "2021-04-20-netflix"
```

```{r}
library(tidyverse)
library(ggrepel)
```


Possible things to look at: 

Number of shows by country by year
```{r}
netflix %>% 
  count(country) %>%
  filter(n > 1) %>%
  arrange(desc(n))
```

```{r}
netflix %>% 
  count(country) %>%
  slice_max(order_by = n, n = 50) %>%
  arrange(desc(n)) %>%
  ggplot(aes(n, reorder(country, n)))+
  geom_col()
```

How old are the shows on Netflix? 
```{r}
netflix %>%
  count(release_year)%>%
  arrange(desc(n))
```
Looks like the number of shows on netflix pretty solidly tracks age of the show. 
```{r}
netflix %>%
  count(release_year) %>%
  ggplot(aes(release_year, n, label = release_year))+
  geom_point()+
  scale_y_log10()+
  geom_text_repel()
```
Most shows are very recent, with the most titles released a couple years back. 

Growth over time by country? 


Maybe look at what words are most likely to be in the descriptions for each country?

Genres by country?
```{r}
interested <- netflix %>%
  count(country) %>%
  slice_max(order_by = n, n = 10)
netflix %>%
  filter(country %in% interested$country) %>%
  group_by(country) %>%
  count(listed_in) %>%
  ggplot(aes(n, listed_in))+
  geom_col()+
  facet_wrap(~country)
```
Woah that is a mess. OK it looks like listed_in has too many unique values. Let's try and separate: 


Could be interesting to look at the gap between release year and date added. Maybe add a by country to that as well? 


# Following David Robinson on youtube
```{r}
netflix %>%
  filter(!is.na(country)) %>%
  count(country= fct_lump(country, 19),
        type,
        sort = TRUE) %>%
  mutate(country = fct_reorder(country, n)) %>%
  ggplot(aes(n, country, fill = type)) +
  geom_col()
```

# let's try and get top genres by country 

Japan data, to check
```{r}
netflix %>% filter(country == "Japan") %>% separate_rows(listed_in, sep = ", ")%>%count(listed_in, sort = TRUE)
```

```{r}
library(tidytext)

width <- 6
title_font <- "Noto Sans Bold"
main_font <- "NotoSans"

theme_set(theme_minimal())
theme <- theme_update(
  text = element_text(family = main_font),
  plot.title = element_text(family = title_font, size = 14),
  plot.title.position = "plot",
  legend.position = "none",
  axis.title = element_text(size = 8),
  axis.text = element_text(size = 8),
  axis.title.x = element_text(family = main_font),
  axis.title.y = element_text(family = main_font),
  plot.caption = element_text(family = main_font, size = 8),
  plot.margin = margin(20,20,20,20)
  #plot.background = element_rect(fill = "#eceff4")
)

netflix %>%
  filter(!is.na(country))%>%
  separate_rows(listed_in, sep = ", ") %>%
  filter(! listed_in %in% c("International TV Shows", "International Movies")) %>%
  count(country = fct_lump(country, 5), listed_in) %>%
  group_by(country) %>%
  slice_max(order_by = n, n = 5)%>%
  ungroup() %>%
  #mutate(listed_in = reorder_within(listed_in, n, country)) %>%
  ggplot(aes(n, reorder_within(listed_in, n, country), fill = country))+
  geom_col(show.legend = FALSE)+
  facet_wrap(~country, scales="free", ncol = 2)+
  scale_y_reordered()+
  labs(
    title = "What kinds of shows do Netflix buy?",
    subtitle = "Most common genres from the top five countries on Netflix.",
    caption = "Excluding 'International TV Shows' and 'International Movies'",
    x = "Number of shows per genre",
    y = NULL
  ) + 
  ggsave("figs/netflix.png", width = width, height = (width*.618)*2)
  
```

