---
title: "2021-04-20-netflix-analysis"
author: "Ben Leamon"
date: "2021-04-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 2021-04-20 Tidy Tuesday: Netflix
```{r}
tuesdata <- tidytuesdayR::tt_load("2021-04-20")
netflix <- tuesdata$netflix_titles
```
proj_path <- "2021-04-20-netflix"

```{r}
library(tidyverse)
library(ggrepel)
```


Possible things to look at: 

Number of shows by country by year
```{r}
netflix %>% 
  count(country) %>%
  filter(n > 1) %>%
  arrange(desc(n))
```

```{r}
netflix %>% 
  count(country) %>%
  slice_max(order_by = n, n = 50) %>%
  arrange(desc(n)) %>%
  ggplot(aes(n, reorder(country, n)))+
  geom_col()
```

Maybe look at what words are most likely to be in the descriptions for each country? Genres by country? Growth over time by country? 

Could be interesting to look at the gap between release year and date added. Maybe add a by country to that as well? 
```{r}
netflix %>%
  count(release_year)%>%
  arrange(desc(n))
```
Looks like the number of shows on netflix pretty solidly tracks age of the show. 
```{r}
netflix %>%
  count(release_year) %>%
  ggplot(aes(release_year, n, label = release_year))+
  geom_point()+
  scale_y_log10()+
  geom_text_repel()
```
Most shows are very recent, with the most titles released a couple years back. 
