---
title: "animal-outcomes-analysis"
author: "Ben Leamon"
date: "23/07/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```

```{r}
tuesdata <- tidytuesdayR::tt_load('2020-07-21')
```
```{r}
animal_complaints <- tuesdata$animal_complaints
```

Let's look at complaints first. What animals do we have? 
```{r}
animal_complaints %>%
  count(`Animal Type`)
```
Lots more dogs than cats, what are the cats getting up to?
```{r}
animal_complaints %>%
  filter(`Animal Type` == "cat") %>%
  count(`Complaint Type`, sort = TRUE)
```
Hmm... Nothing too juicy.

Let's see if Brisbane has got anything fun.
```{r}
brisbane <- tuesdata$brisbane_complaints
brisbane %>%
  count(animal_type, sort = TRUE)
```
Let's have a look at what the "Other animal" categories are. 
```{r}
brisbane%>%
  filter(animal_type == "Other Animal") %>%
  count(category, sort = TRUE)
```
Ok well it doesn't seem like there's a place where we can conlcusively see what the animals in the complaint are. Most are foxes, nuisances, or deer though. Not going to lie, I was kind of hoping for some weird dagerous animals. 

Let's go to the general outcomes sheet. This is probably the one I'll end up looking at.

```{r}
outcomes <- tuesdata$animal_outcomes
```

What animals are most common
```{r}
outcomes %>%
  count(animal_type, sort = TRUE)
```
Oh, duh, these are yearly totals. 

```{r}
outcomes %>%
  group_by(year, animal_type) %>%
  ggplot(aes(year, Total, fill = animal_type))+
  geom_bar(stat = "identity", position = "dodge")
```

Let's look at the total number of animals that the RSPCA deals with in a given year. 
```{r}
totals <- outcomes %>%
  group_by(year, animal_type) %>%
  summarise(species_total = sum(Total))

grand_total <- totals %>%
  filter( is.na(species_total) == FALSE)%>%
  group_by(year)%>%
  summarise(grand_total = sum(species_total))
```

```{r}
ggplot(grand_total, aes(year, grand_total))+
  geom_line()+
  expand_limits(y =0)
```
Total numbers fell a lot after 2010.

Total number of animals who interact with the system by species by year:
```{r}
totals %>%
  ggplot(aes(year, species_total, color = animal_type))+
  geom_line()
```
Dogs and cats both had really high numbers around 2008. I wonder if that had to do iwth the financial crisis?

What happens to each of these species? 
```{r}
outcomes%>% 
  group_by(year, animal_type) %>%
  ggplot(aes(year, Total, color = outcome))+
  geom_line()+
  facet_wrap(~animal_type, scales = "free_y")
  
```
OK this is looking a bit promising, not sure I like the free scales though. I think I need to change this into a proportion. 

```{r}
prop <- outcomes %>%
  group_by(year, animal_type) %>%
  summarise(species_total = sum(Total))

 outcomes_prop<- inner_join(outcomes, outcomes_prop) %>%
   mutate(prop = Total / species_total)
 
outcomes_prop %>%
  group_by(year, animal_type)%>%
  ggplot(aes(year, prop, color = outcome))+
  geom_line()+
  facet_wrap(~animal_type)
```
I think this is probalbly where I'll leave it. 
